SAT Competition 2020\tnoteref{title}

### 2020-12-17 paper/main.tex
edited some tables

@@

Table~\ref{tab:families} displays the numbers of submitted, interesting and finally selected instances grouped by problem family.

\begin{table}[h]
\centering
\begin{tabular}{rrr||l}
submitted & interesting & selected & family\\
\hline\hline
6 & 2 & 2 & 01-integer-programming\\
187 & 139 & 14 & antibandwidth\\
40 & 20 & 13 & baseball-lineup\\
393 & 333 & 14 & bitvector\\
20 & 15 & 12 & cellular-automata\\
38 & 18 & 7 & cnf-miter\\
14 & 14 & 14 & coloring\\
20 & 20 & 14 & core-based-generator\\
18 & 13 & 13 & cover\\
106 & 93 & 34 & cryptography\\
20 & 19 & 7 & discrete-logarithm\\
58 & 57 & 7 & edge-matching\\
8 & 5 & 5 & fermat\\
40 & 3 & 0 & flood-it-puzzle\\
20 & 19 & 13 & hgen\\
56 & 48 & 14 & hypertree-decomposition\\
20 & 16 & 14 & influence-maximization\\
20 & 20 & 9 & lam-discrete-geometry\\
20 & 20 & 8 & polynomial-multiplication\\
4 & 2 & 2 & schur-coloring\\
20 & 20 & 12 & station-repacking\\
23 & 19 & 7 & stedman-triples\\
5 & 2 & 2 & sum-subset\\
20 & 20 & 14 & tensors\\
12 & 7 & 7 & termination\\
20 & 16 & 14 & timetable\\
16 & 16 & 14 & tournament\\
36 & 36 & 14 & vlsat\\
\hline
1260 & 1012 & 300 & $\Sigma$
\end{tabular}
\caption{Families and amounts of newly submitted instances}
\label{tab:families}
\end{table}

\begin{table}[h]
\centering
\begin{tabular}{c||ccc|c}
 & SAT & UNSAT & UNKNOWN & $\Sigma$\\
\hline\hline
new instances & 114 & 78 & 108 & 300 \\
old instances & 21 & 57 & 22 & 100\\
\hline
$\Sigma$ & 135 & 135 & 130 & 400
\end{tabular}
\caption{Amount of old and new instances by result}
\label{tab:final}
\end{table}

@@

Another successful string of development is rooted in the CoMinisatPS fork of Minisat by Chanseok Oh~\cite{}. 
Maple first emerged as a series of forks submitted to SAT Competition 2016, introducing the two new branching heuristics Learning Rate based Branching (LRB) and Conflict History based Branching (CHB)~\cite{}. 
The then award winning variant MapleCOMSPS is an implementation of the LRB heuristic on top of CoMinisatPS~\cite{}. 
The award winning derivatives of MapleCOMSPS in SAT Competition 2017 include a new Learnt Clause Minimization (LCM) procedure and the new branching heuristic Distance (Dist). 
This was extended with case-based Chronological Backtracking (ChronoBT) by Ryvchin and Nadel~\cite{}, which resulted in the award winning solver Maple\_LCM\_Dist\_ChronoBT of SAT Competition 2018~\cite{}. 
Its extension MapleLCMDistChronoBT-DL with a new clause learning/forgetting heuristic Duplicate Learnts (DL)~\cite{} won SAT Race 2019. 
The success story of Maple resulted also in numerous submissions of modified Maple solvers in this competition, some of which have been successful (see Section~\ref{}).

@@

\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{ExMapleLCMDistCBT} & padc\_dl & \\
 &  & padc\_dl\_ovau\_lin & \\
 &  & padc\_dl\_ovau\_exp & \\
 &  & psids\_dl & \\
% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

>>>>

\begin{table}[t]
\small
\centering
\begin{tabular}{|l|l||rr|}
\hline
Family & Author & Submitted & Selected\\
\hline\hline
0-1 Integer Programming & Riveros & 6 & 2 \\
Anti-Bandwidth & Biere & 187 & 14 \\
Baseball Lineup & Hickey & 40 & 13 \\
Bit-Vector & Preiner & 393 & 14 \\
Cellular Automata & Chowdhury & 20 & 12 \\
CNF Miter & Manthey & 38 & 7 \\
Coloring & Oostema & 14 & 14 \\
Core-based Generator & Hartung & 20 & 14 \\
Cover & Gacek & 18 & 13 \\
Cryptography & Paxian, Shaw, Soos & 106 & 34 \\
Discrete Logarithm & Jingchao & 20 & 7 \\
Edge Matching & Holten & 58 & 7 \\
Fermat & Riveros & 8 & 5 \\
Flood-It Puzzle & Stiphout & 40 & 0 \\
HGen & Guanfeng & 20 & 13 \\
Hypertree Decomposition & Schidler & 56 & 14 \\
Influence Maximization & Kochemazov & 20 & 14 \\
Lam Discrete Geometry & Nejati & 20 & 9 \\
Polynomial Multiplication & Maoluo & 20 & 8 \\
Schur Coloring & Riveros & 4 & 2 \\
Station Repacking & Newman & 20 & 12 \\
Stedman Triples & Johnson & 23 & 7 \\
Sum Subset & Riveros & 5 & 2 \\
Tensors & Savicky & 20 & 14 \\
Termination & Yolcu & 12 & 7 \\
Timetable & Djamegni & 20 & 14 \\
Tournament & Heule & 16 & 14 \\
Vlsat & Bouvier & 36 & 14 \\
\hline
\multicolumn{2}{|r||}{$\Sigma$} & 1260 & 300 \\
\hline
\end{tabular}
\caption{Families and amounts of newly submitted instances}
\label{tab:families}
\end{table}

@@

Table~\ref{tab:families} displays the numbers of submitted and selected instances grouped by problem family and author.

\begin{table}[t]
\centering
\begin{tabular}{|r|ccc|c|}
\hline
 & SAT & UNSAT & UNKNOWN & $\Sigma$\\
\hline\hline
New Instances & 114 & 78 & 108 & 300 \\
Old Instances & 21 & 57 & 22 & 100\\
\hline
$\Sigma$ & 135 & 135 & 130 & 400\\
\hline
\end{tabular}
\caption{Amount of old and new instances by result}
\label{tab:final}
\end{table}

@@

Another successful string of development is rooted in the CoMinisatPS fork of Minisat by Chanseok Oh~\cite{}. 
Maple first emerged as a series of forks submitted to SAT Competition 2016, introducing the two new branching heuristics Learning Rate based Branching (LRB) and Conflict History based Branching (CHB)~\cite{}. 
The then award winning variant MapleCOMSPS is an implementation of the LRB heuristic on top of CoMinisatPS~\cite{}. 
The next award winning derivative Maple\_LCM\_Dist in SAT Competition 2017 came with a new Learnt Clause Minimization (LCM) procedure and the new branching heuristic Distance (Dist). 
This was extended with case-based Chronological Backtracking (ChronoBT) by Ryvchin and Nadel~\cite{}, which resulted in the award winning solver Maple\_LCM\_Dist\_ChronoBT of SAT Competition 2018~\cite{}. 
Its extension MapleLCMDistChronoBT-DL with a new clause learning/forgetting heuristic Duplicate Learnts (DL)~\cite{} won SAT Race 2019. 
The success story of Maple resulted also in numerous submissions of modified Maple solvers in this competition, some of which have been successful (see Section~\ref{}).

@@

\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{MapleLCMDistCBT} & padc\_dl & \\
 &  & padc\_dl\_ovau\_lin & \\
 &  & padc\_dl\_ovau\_exp & \\
 &  & psids\_dl & \\
% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline
